The imprint of global magma oceans on exoplanet demographics

### 2022-08-22 src/tex/ms.tex
add example plot of N_mo_detections, caption

@@

\subsection{Mission design trades}\label{sec:mission-design-trades}
\citet{Penny2019} mention that a significant increase in planet yield could be achieved if the telescope's slew speed was increased.

>>>>

\subsection{Statistical power of different mission designs}\label{sec:statpower_missions}
\todo[inline]{show detectability of the magma ocean signature for different mission designs}

\begin{figure}[ht!]
%    \script{figurescript.py}
    \begin{centering}

        \includegraphics[width=\linewidth]{figures/example_Ndetected_surveys.pdf}
        \caption{
        Detections of magma ocean-bearing planets as a function of magma ocean occurrence for different survey designs.
        }
        \label{fig:example_Ndetected_surveys}
    \end{centering}
\end{figure}

@@

\subsection{Mission design trades}\label{sec:mission-design-trades}
\todo[inline]{Maps to Sect. \ref{sec:statpower_missions}.}
\citet{Penny2019} mention that a significant increase in planet yield could be achieved if the telescope's slew speed was increased.
